Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
what does ASSR mean ?

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC tasks.

Thus, studying the first DCASE challenge \cite{barchiesi2015acoustic} in 2013 is convenient as it concentrates much of the effort for this latter task. The table \ref{tab:dcase} summarizes the different algorithmic choices taken by the teams. Unless otherwise stated, scene predictions are achieved by majority voting of predictions \ml{gregoire ?}.

>>>>

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR \vl{acronym ?}, much of the work dedicated to acoustic scene modeling is applied to ASC tasks.
Thus, studying the first DCASE challenge \cite{barchiesi2015acoustic} in 2013 is convenient as it concentrates much of the effort for this latter task. The table \ref{tab:dcase} summarizes the different algorithmic choices taken by the teams. Unless otherwise stated, scene predictions are achieved by majority voting of predictions \ml{gregoire ?}.
